Neutral ISM, Lyman-Alpha and Lyman-continuum in nearby starburst Haro 11

### 2016-11-22 Paper/Paper.tex
Almost all comments implemented
Also corrected method for inferring effective HI column density for Lyman Continuum; this should be integrated over all velocities for Lyman Continuum but only be taken around line center for Ly$\alpha$

\begin{abstract}
Star forming galaxies are believed to be the main source of ionizing
radiation responsible for reionizing the early Universe. Direct
observations of escaping ionizing radiation have however been few and
with escape fractions far below what would be necessary to account for
the ionization history of the Universe. In the local Universe, only a
few handfuls of emitters have been observed with typical escape
fractions of a few percent. It seems the mechanisms regulating this
escape need to be strongly evolving with redshift, if galaxies are to be
held responsible for reionization. Gas mass, star formation feedback and
thus star formation activity are among the main suspect parameters,
known to both regulate neutral gas coverage and evolve with cosmic time.
In this paper, we present a reanalysis of far-UV HST-COS spectra of the
first detected Lyman-continuum leaker in the local Universe, Haro 11, in
which we examine the connections between Lyman-continuum leakage and
Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
like kinematics, geometry and column density. We discuss the two
extremes of an optically thin, density bounded ISM and a riddled,
optically thick, ionization bounded ISM and how Haro 11 fits into the
theoretical predictions made from these models. We find that the most
likely ISM model for Haro 11 knot C is one of clumpy neutral medium
embedded in a highly ionized inter-clump medium with a combined covering
fraction of unity and a residual neutral gas column density in the
ionized medium of
$5 \times 10^{13} \leq N_{\rm HI} \leq 3 \times 10^{16}$; high enough to
be optically thick to Lyman-$\alpha$, but low enough to be at least
partly transparent to Lyman-continuum and undetectable in Si\textsc{ii}.
\end{abstract}

@@

In any given velocity bin, the line intensity in terms of the continuum
intensity is given as

%
\begin{equation*}
\frac{I}{I_0} = 1 - f_C (1 - e^{-\tau}), 
\end{equation*}
%

with the optical depth $\tau$ given as:

%
\begin{equation*}
\tau = f\lambda \frac{\pi e^2}{m_e c} N 
       = f\lambda \frac{N}{3.768 \times 10^{14}} 
\end{equation*}
%

Here, $f$ is the oscillator strength of a given transition, $\lambda$ is
its rest frame wavelength in Å, $N = N(v)$ is the column density of the
relevant ion \emph{within the given velocity bin}, and $f_{C}$ is the
covering fraction of neutral gas \emph{moving at the given velocity}.
When multiple absorption lines are present which arise from the same
ground state; the population of this state is the same for all
transitions, and their relative strengths are governed simply by their
oscillator strengths, and with two or more such transitions, $f_{C}$ and
$N$ can be inferred from knowledge of $f \lambda$ and measured values of
$I/I_0$.

@@

It is also worth noting that \ion{C}{2} has a significantly higher
ionization potential than \ion{Si}{2}, such that the former will be more
abundant in regions of higher ionization, with \ion{C}{2} in effect
tracing slightly different regions than \ion{Si}{2}. Furthermore, in
these regions of higher ionization, the relative level populations of
the Carbon ground state can be significantly altered by shifts in
e.g.~electron density and radiation field, which can alter the line
shape further. We make no attempt at mapping these complex conditions
here, but note only that there exists a range of non-exotic physical
effects which can generate the deeper and wider $\lambda 1334$ profile
we observe while still being compatible with the ISM being optically
thick in $\lambda 1260$.

@@

\begin{figure}
\centering
\includegraphics[width=3.500in]{../Figs/LyACoverfracs.pdf}
\caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
approximate units of the surrounding continuum level. Full line is the
measured values smoothed by a 5 px. flat kernel; surrounding shading
encloses the $\pm 1 \sigma$ error band. \textbf{Middle panel}: Black
steps show the averaged, LIS line profile, smoothed by a 5px kernel.
Surrounding gray shading denotes the $\pm 1 \sigma$ confidence band.
\textbf{Lower panel}: Same as middle panel, but for the \ion{Si}{4}
transitions. }\label{fig:HisLisLya}
\end{figure}

The picture is what we would expect from a Lyman Continuum leaker: weak
neutral and strong ionized absorption profiles, the latter almost
everywhere consistent with full coverage, reveal a highly ionized medium
in front of the central cluster. This is also in good agreement with the
findings of Pardy et al. (submitted), who conclude that the galaxy has
about twice as much ionized as neutral gas. In addition to this, it is
interesting to note the close similarity in shape between the
\ion{Si}{2} and \ion{Si}{4} line profiles, indicating that they likely
originate in the same higher density regions. These regions will likely
be ionized on the side facing the central cluster, being photoionized by
its hot, massive stars. This also implies that the nebular emission
outflow found in {[}Rivera-Thorsen et al, submitted{]} at least
partially traces the same gas as the \ion{Si}{4} absorption here and, by
extension, also the neutral medium. Looking at
fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
largest amount of gas in a single velocity bin for both phases is found
at around $v \approx -50$ km s⁻¹, where also a component is found in
{[}Rivera-Thorsen et al., submitted{]}. The outflow velocity
$v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
Interestingly, \citet{Sandberg2013} found from the neutral Sodium
resonance absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an
overall, weak \emph{redshift} of $v = 32$ km s⁻¹, strongly at odds with
the blueshift of $v = 149$ km s⁻¹ found in this work. We note that Na
\textsc{i} has a very low ionization potential of only $\sim 5$ eV,
meaning that these atoms may well only be present in fractions of the
gas traced by Si \textsc{ii}. This is in agreement with the finding of
\citet{Sandberg2013} that NaD, despite being a strong transition, shows
absorption of only $\sim 95\%$ of continuum level. They also find that
NaD is mostly found in small, optically thick clouds, further supporting
this interpretation.

Also the absorption feature in the Lyman $\alpha$ profile in the upper
panel seems to morphologically follow the shape of the metal lines,
indicating that radiative transfer effects are modest, indicative of a
fairly low column density of HI. We find a Lyman $\alpha$ peak velocity
of $v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$ km s⁻¹ w.r.t the
H$\alpha$-derived systemic velocity found by \citet{Sandberg2013}. This
velocity, as it is also discussed in \citet{Verhamme2015}, is just
consistent with their theoretical predictions for a density-bounded,
low-column density system, albeit on the upper limit of their allowed
range.

@@

Lyman $\alpha$ escape is mainly governed by gas at or near systemic
velocity. In the middle panel of fig.~\ref{fig:WithColDens} (a) is shown
the best-fit column density $N_{\rm Si II}$ for each velocity bin. The
value at systemic velocity is $\log_{10}(N_{\rm Si II}) = 12.1 \pm 0.2$.
We adapt the value for local starbursts of log(Si/O) $= -1.59 \pm 0.07$
from \citet{Garnett1995}, and use this to estimate the column density of
neutral Hydrogen in front of the light source in the same way is in
{[}Puschnig et al., submitted to MNRAS{]} as follows. \citet{Guseva2012}
found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
With $\log_{10}$ Si/O $= -1.59 \pm 0.07$, this leads to a Si/H ratio in
the neutral medium of $Si / H = 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
$\log N \sim 17$, this range is not consistent with the low- optical
depth, density bounded scenario.

However, the pure riddled ionization bounded scenario is easily ruled
out since the Ly$\alpha$ profile does not have any appreciable component
at zero velocity. We expect a residual neutral fraction to remain in the
ionized, inter-clump phase; a fraction which has a column density high
enough to block Ly$\alpha$ efficiently at line center, but low enough to
be at least part transparent to LyC radiation. In Puschnig et al.
(submitted), it was shown for Tololo 1247-232, an object with very
similar \ion{Si}{2} column densities, that the sensitivity limit for
\ion{Si}{2} is $\sim 1 \times 10^{11}$ cm\textsuperscript{-2}, which
with the metallicity for Haro 11 C corresponds to
$N_{\text{H\textsc{i}}} \sim 3.1 \times 10^{16}$ cm\textsuperscript{-2}.
This leaves around 2-3 orders of magnitude in $N$, in which the gas has
no detectable \ion{Si}{2} and is optically thick to Ly$\alpha$ and
translucent to Lyman Continuum.

This result seems to be consistent with what is found in the Green Pea
galaxies of \citep{Henry2015} - these galaxies have sometimes very low
LIS optical depth, which is usually indicative of low covering fractions
and high porosity of the neytral medium - and yet they find covering
fractions of near unity of \ion{H}{1} from Lyman $\beta$ absorption,
indicating column densities of $N \gtrsim 10^{16}$. Like in the case of
Haro 11, this indicates that a non-negligible neutral component must be
present in the ionized phase, although it may very well be of such low
densities and metallicity that metal absorption from this medium is
undetectable.

The column densities we derive for \ion{Si}{2} in this work are
generally between $12.0 \lesssim \log N \lesssim 12.5$, column densities
around which the transitions involved become optically thick: For
$\lambda \lambda 1260, 1526 \text{and} 1304$, $tau$ becomes 1 at
$\log N \sim 11.3, 12.2$ and $12.5$, respectively. In the line wings,
and in particular at $v_0$, only $\lambda 1260$ seems to be optically
thick, and it seems the column densities arrived at can be trusted. But
at line center, around $v\sim v_{int}$, the column densities found are
so close to the limit that they are most likely to be interpreted as
lower limits. There might also be systematics in the determination of
the continuum around the lines which may lead to the lines at
$\lambda \lambda 1304, 1526$ to be falsely seen as shallower than
$\lambda 1260$, meaning that all computed column densities are really
lower limits rather than actual values. The confidence intervals in fig.
\ref{fig:WithColDens} do \emph{not} reflect this possible saturation,
but only the formal errors from the best approximation to the residual
intensity, they do not include systematics.

If the computed column densities are in fact lower limits, this means
the inferred \ion{H}{1} column densities are also lower limits. This
would rule out the marginal possibility that the clumps themselves are
partly transparent to Lyman Continuum, and strengthen the riddled,
ionization-bounded medium scenario that the ISM on the line of sight to
Haro 11 C consists of dense, neutral clumps with an ionized interclump
medium containing a dilute neutral component.

@@

The exact value of the metallicity is however uncertain. The values
found from nebular recombination lines by \citet{Guseva2012} are
measured mainly in the central HII regions around the clusters; and
differ by 0.2 dex between knot B and C. The neutral, outflowing gas
could be mixed, or have an unseen LOS distance component larger than the
knot separation, drawing into question which is the better value to
assume for this gas. We base our conclusions on the value found for knot
C, but note that using the metallicity of $12 + \log (O/H) = 8.3$ found
for knot B by \citet{Guseva2012}, the inferred H \textsc{i} column
densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
However, the question of the exact metallicity of the outflowing gas is
complicated. Gas closer to the star forming regions is expected to be
more strongly enriched than gas further away, which would imply that the
HI column density is \emph{larger} than inferred from \ion{Si}{2} above.
To this can be added the further complication stemming from the merger
event that the galaxy is currently undergoing, which may have mixed gas
of different metal contents thoroughly. In any case, though, we would
expect the regions nearest to the starbursts to generally have higher
metallicity than the surrounding cool gas, such that the HI column
density inferred above is more likely to be underestimated than
overestimated.

@@

@@

We confirm previous authors concluding that the medium is highly ionized
with clumps of neutral gas of low velocity-binned covering fraction,
increasing the probability of finding direct sight lines between these.
The clumps have low HI column densities in the range
$N_{\rm HI} = 6.2^{+0.9}_{-1.1} \times 10^{17}$ given the metallicity of
the background HII region, which is likely a slight underestimate of
$N_{\rm HI}$. There is a possibility that the found column densities are
in fact lower limits, since the found \ion{Si}{2} column densities are
close to the limit where this ion becomes optically thick. We therefore
conclude that the leaked ionizing photons, if originating from this
cluster, most likely escaped via sight lines through the ionized medium,
which must thus contain a neutral gas column density
$5 \times 10^{13} \leq N_{\rm HI}^{\rm HIS} \leq 3 \times 10^{16}$. This
range is bounded downwards by the value at which HI becomes transparent
to Lyman-$\alpha$, and upwards by the sensitivity to \ion{Si}{2}.

@@

G.Ö. is a Royal Swedish Academy of Science research fellow (supported by
a grant from the Knut \& Alice Wallenbergs foundation). M.H.
acknowledges the support of the Swedish Research Council,
Vetenskapsrådet, and the Swedish National Space Board (SNSB) and is
Academy Fellow of the Knut and Alice Wallenberg Foundation. This project
has made extensive use of the Python-based packages Numpy \citep{Numpy},
SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib}, Pandas
\citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
\citep{Astropy2013}.

>>>>

\begin{abstract}
Star forming galaxies are believed to be a major source of ionizing
radiation responsible for reionizing the early Universe. Direct
observations of escaping ionizing radiation have however been few and
with escape fractions far below what would be necessary to account for
the ionization history of the Universe. In the local Universe, only a
few handfuls of emitters have been observed with typical escape
fractions of a few percent. It seems the mechanisms regulating this
escape need to be strongly evolving with redshift, if galaxies are to be
held responsible for reionization. Gas mass, star formation feedback and
thus star formation activity are among the main suspect parameters,
known to both regulate neutral gas coverage and evolve with cosmic time.
In this paper, we present a reanalysis of far-UV HST-COS spectra of the
first detected Lyman-continuum leaker in the local Universe, Haro 11, in
which we examine the connections between Lyman-continuum leakage and
Lyman-$\alpha$ line shape and feedback-influenced neutral ISM properties
like kinematics, geometry and column density. We discuss the two
extremes of an optically thin, density bounded ISM and a riddled,
optically thick, ionization bounded ISM and how Haro 11 fits into the
theoretical predictions made from these models. We find that the most
likely ISM model for Haro 11 knot C is one of clumpy neutral medium
embedded in a highly ionized inter-clump medium with a combined covering
fraction of unity and a residual neutral gas column density in the
ionized medium of
$5 \times 10^{13} \leq N_{\rm HI} \leq 4 \times 10^{15}$; high enough to
be optically thick to Lyman-$\alpha$, but low enough to be at least
partly transparent to Lyman-continuum and undetected in Si\textsc{ii}.
\end{abstract}

@@

In any given velocity bin, the line intensity in terms of the continuum
intensity is given as
%
\begin{equation}
\label{eq:II0}
\frac{I}{I_0} = 1 - f_C (1 - e^{-\tau}),
\end{equation}
%
 with the optical depth $\tau$ given as:
%
\begin{equation}
\label{eq:tau}
\tau = f\lambda \frac{\pi e^2}{m_e c} N 
       = f\lambda \frac{N}{3.768 \times 10^{14}}
\end{equation}
%
 Here, $f$ is the oscillator strength of a given transition, $\lambda$
is its rest frame wavelength in Å, $N = N(v)$ is the column density of
the relevant ion \emph{within the given velocity bin}, and $f_{C}$ is
the covering fraction of neutral gas \emph{moving at the given
velocity}. When multiple absorption lines are present which arise from
the same ground state; the population of this state is the same for all
transitions, and their relative strengths are governed simply by their
oscillator strengths, and with two or more such transitions, $f_{C}$ and
$N$ can be inferred from knowledge of $f \lambda$ and measured values of
$I/I_0$.

@@

@@

\begin{figure}
\centering
\includegraphics[width=3.500in]{../Figs/LyACoverfracs.pdf}
\caption{\textbf{Upper panel}: Ly$\alpha$ profile of Haro 11 C, in
approximate units of the surrounding continuum level. Full line is the
measured values smoothed by a 5 px. flat kernel; surrounding shading
encloses the $\pm 1 \sigma$ error band (mostly comparable in width to
the line width). \textbf{Middle panel}: Black steps show the averaged,
LIS line profile, smoothed by a 5px kernel. Surrounding gray shading
denotes the $\pm 1 \sigma$ confidence band. \textbf{Lower panel}: Same
as middle panel, but for the \ion{Si}{4} transitions.
}\label{fig:HisLisLya}
\end{figure}

The picture is what we would expect from a Lyman Continuum leaker: weak
neutral and strong ionized absorption profiles, the latter almost
everywhere consistent with full coverage, reveal a highly ionized medium
in front of the central cluster. This is also in good agreement with the
findings of \citet{Pardy2016arXiv}, who conclude that the galaxy has
about twice as much ionized as neutral gas. In addition to this, it is
interesting to note the close similarity in shape between the
\ion{Si}{2} and \ion{Si}{4} line profiles, indicating that they likely
represent two different phases in the same higher density regions. These
regions will likely be ionized on the side facing the central cluster,
being photoionized by its hot, massive stars. This also implies that the
nebular emission outflow found in {[}Rivera-Thorsen et al, submitted{]}
at least partially traces the same gas as the \ion{Si}{4} absorption
here and, by extension, also the neutral medium. Looking at
fig.~\ref{fig:SingleLines}, we see that maximum absorption and thus the
largest amount of gas in a single velocity bin for both phases is found
at around $v \approx -50$ km s⁻¹, where also a component is found in
{[}Rivera-Thorsen et al., submitted{]}. The outflow velocity
$v_{\text{int}}$ is at 149 ± 7 km s⁻¹, fully consistent with the
findings of \citet{Heckman2015} and \citet{Alexandroff2015}.
Interestingly, \citet{Sandberg2013} found from the neutral Sodium
resonance absorption doublet $\lambda \lambda 5889.95,5895.92$ (NaD) an
overall, weak \emph{redshift} of $v = 32$ km s⁻¹. From
e.g.~fig.~\ref{fig:HisLisLya}, it is evident that while neutral gas
\emph{is} present at these velocities, the velocity is at odds with the
integrated velocity of $v = -149$ km s⁻¹ found in this work. We note
that Na \textsc{i} has a very low ionization potential of only $\sim 5$
eV, meaning that these atoms may well only be present in the densest
and/or dustiest regions, in which Sodium is shielded from ionization.
This is in agreement with the finding of \citet{Sandberg2013} that NaD,
despite being a strong transition, shows absorption of only $\sim 95\%$
of continuum level and is mostly found in small, optically thick clouds.
This suggests that the NaD is tracing only the densest and/or dustiest
regions which are more slowly accelerated by star formation feedback
than the surrounding, more dilute medium. In fig.~\ref{fig:apert}, dusty
regions in the aperture are apparent E and W of knot C, and in the
better resolution of fig. 1 in \citet{Adamo2010}, these regions seem
like they might be connected by a narrow dust lane partially covering
the background source. We speculate that the NaD absorption of
\citet{Sandberg2013} might be associated with this.

Also the absorption feature in the Lyman $\alpha$ profile in the upper
panel seems to morphologically follow the shape of the metal lines,
indicating that radiative transfer effects are modest, indicative of a
fairly low column density of HI around line center. We find a Lyman
$\alpha$ peak velocity of $v_{\rm peak}^{\mathrm{Ly}\alpha} = 158 \pm 1$
km s⁻¹ w.r.t the systemic velocity found by \citet{Sandberg2013},
derived from nebular emission lines in the region around knot C. This
velocity, as it is also discussed in \citet{Verhamme2015}, is just
consistent with their theoretical predictions for a density-bounded,
low-column density system, albeit on the upper limit of their allowed
range.

@@

Lyman $\alpha$ escape is mainly governed by gas at or near systemic
velocity. In the middle panel of fig.~\ref{fig:WithColDens} (a) is shown
the best-fit column density $N_{\rm Si II}$ for each velocity bin. The
value at systemic velocity is $\log_{10}(N_{\rm Si II}) = 12.1 \pm 0.2$.
We adapt the value for local starbursts of log(Si/O) $= -1.59 \pm 0.07$
from \citet{Garnett1995}, and use this to estimate the column density of
neutral Hydrogen in front of the light source in the same way is in
{[}Puschnig et al., submitted to MNRAS{]} as follows. \citet{Guseva2012}
found a metallicity of Haro 11 C of $12 + \log_{10}(\text{O/H}) = 8.1$.
With $\log_{10}$ Si/O $= -1.59 \pm 0.07$, this leads to a Si/H ratio in
the neutral medium of Si / H $= 3.24^{+0.57}_{-0.48} 10^{-6}$, leading
to a Hydrogen column density of $6.2^{+0.9}_{-1.1} \times 10^{17}$
cm\textsuperscript{-2}. Since HI gets opaque to ionizing radiation at
$\log N \sim 17.2$ \citep{Verhamme2015}, this range is not consistent
with the low- optical depth, density bounded scenario. Furthermore;
while Ly$\alpha$ radiative transfer is dominated by gas of $v \sim v_0$,
Lyman continuum is sensitive to \ion{H}{1} at \emph{all} velocities.
Integrating the computed column densities over $-450$ km s⁻¹ $< v < 150$
km s⁻¹, the velocity range over which the column densities can be
reasonably well determined (and removing the unphysically high value in
the bin at $v \approx 222$ km s⁻¹), yields a conservative estimate of
$\log N_{\rm Si II} \approx 19.4$, corresponding to more than 150
optical depths in Lyman Continuum, strongly incompatible with an
optically thin, density-bounded scenario.

However, the pure riddled ionization bounded scenario is easily ruled
out since the Ly$\alpha$ profile does not have any appreciable emission
component at zero velocity. We therefore expect a residual neutral
fraction to remain in the ionized phase; a fraction which has a column
density high enough to block Ly$\alpha$ efficiently at line center, but
low enough to be at least part transparent to Lyman Continuum radiation
and undetected in \ion{Si}{2}.

We can estimate the lowest detectable $N_{\rm Si II}$ by noting that the
relative errors for the \ion{Si}{2} lines in our spectrum are
$\sim 0.05$. Assuming a covering fraction of unity for the dilute
neutral component, and adopting the oscillator strength of the strongest
of the \ion{Si}{2} transitions, $f\lambda_{1260 \AA} = 1486.8$, we find
in the limit that $I/I_0 = e^{-\tau} = 0.95$, and eq.~\ref{eq:tau}
becomes:
%
\begin{equation}
\label{eq:silim}
N_{\rm Si II}^{\rm min} = -\log_{e}(0.95) \frac{3.768 \times 10^{14}}{f\lambda} 
    = 10^{10.1} \text{cm}^{-2},
\end{equation}
%
 which with the adopted metallicity for Haro 11 C corresponds to a
minimum Hydrogen column density of
$N_{\rm HI}^{\rm min} \sim 4.0 \times 10^{15}$ cm⁻². This leaves around
2 orders of magnitude in $N_{\rm H I}$, in which the gas is not detected
in \ion{Si}{2} and is optically thick to Ly$\alpha$ while translucent to
Lyman Continuum. If we require the gas to be detected in at least two of
the lines included in this analysis, the limiting hydrogen column
density becomes $N_{\rm HI}^{\rm min} \sim 4.9 \times 10^{16}$ cm⁻²,
adding another order of magnitude to the allowed range, but we adopt the
lower value as a conservative estimate.

The existence of a diffuse neutral component being present in the
ionized medium seems consistent with what is found in the Green Pea
galaxies of \citep{Henry2015} - these galaxies have sometimes very low
LIS optical depth, which is usually indicative of low covering fractions
and high porosity of the neytral medium - and yet they find covering
fractions of near unity of \ion{H}{1} from Lyman $\beta$ absorption,
indicating column densities of $N \gtrsim 10^{16}$. Like in the case of
Haro 11, this indicates that a non-negligible neutral component must be
present in the ionized phase, although it may very well be of such low
densities and metallicity that metal absorption from this medium is
undetectable.

The column densities we derive for \ion{Si}{2} in this work are
generally between $12.0 \lesssim \log N \lesssim 12.5$, column densities
around which the transitions involved become optically thick: For
$\lambda \lambda 1260, 1526 \text{ and } 1304$, $\tau$ becomes 1 at
$\log N \sim 11.3, 12.2$ and $12.5$, respectively. Off the regions of
strongest absorption, and in particular at $v_0$, only $\lambda 1260$
seems to be optically thick, and it seems the column densities arrived
at can be trusted. But at line center, around $v\sim v_{int}$, the
column densities found are so close to the limit that they are most
likely to be interpreted as lower limits. There might also be
systematics in the determination of the continuum around the lines which
may lead to the lines at $\lambda \lambda 1304, 1526$ to be falsely seen
as shallower than $\lambda 1260$, meaning that all computed column
densities are really lower limits rather than actual values. The
confidence intervals in fig. \ref{fig:WithColDens} do \emph{not} reflect
this possible saturation, but only the formal errors from the best
approximation to the residual intensity, they do not include
systematics.

If the computed column densities are in fact lower limits, this means
the inferred \ion{H}{1} column densities are also lower limits. This
would strengthen the modified riddled, ionization-bounded medium
scenario that the ISM on the line of sight to Haro 11 C consists of
dense, neutral clumps with an ionized interclump medium containing a
dilute neutral component.

@@

The exact value of the metallicity is however uncertain. The values
found from nebular recombination lines by \citet{Guseva2012} are
measured mainly in the central HII regions around the clusters; and
differ by 0.2 dex between knot B and C. The neutral, outflowing gas
could be mixed, or have an unseen LOS distance component larger than the
knot separation, drawing into question which is the better value to
assume for this gas. We base our conclusions on the value found for knot
C, but note that using the metallicity of $12 + \log (O/H) = 8.3$ found
for knot B by \citet{Guseva2012}, the inferred H \textsc{i} column
densities are $3.9 \pm 0.6 \times 10^{17}$ cm\textsuperscript{-2}.
However, the question of the exact metallicity of the outflowing gas is
complicated. Gas closer to the star forming regions is expected to be
more strongly enriched than gas further away, which would imply that the
HI column density is \emph{larger} than inferred from \ion{Si}{2} above.
To this can be added the further complication stemming from the merger
event that the galaxy is currently undergoing, which may have mixed gas
of different metal contents. In any case, though, we would expect the
regions nearest to the starbursts to generally have higher metallicity
than the surrounding cool gas, such that the HI column density inferred
above is more likely to be underestimated than overestimated.

@@

It is also worth noting that \ion{C}{2} has a significantly higher
ionization potential than \ion{Si}{2}, such that the former will be more
abundant in regions of higher ionization, with \ion{C}{2} in effect
tracing slightly different regions than \ion{Si}{2}. Furthermore, in
these regions of higher ionization, the relative level populations of
the Carbon ground state can be significantly altered by shifts in
e.g.~electron density and radiation field, which can alter the line
shape further. We make no attempt at mapping these complex conditions
here, but note only that there exists a range of non-exotic physical
effects which can generate the deeper and wider $\lambda 1334$ profile
we observe while still being compatible with the ISM being optically
thick in \ion{Si}{2} $\lambda 1260$.

@@

We confirm previous authors concluding that the medium is highly ionized
with clumps of neutral gas of low velocity-binned covering fraction,
increasing the probability of finding direct sight lines to the
background star cluster between these. The clumps have HI column
densities of gas around $v=0$ in the range
$N_{\rm HI} = 6.2^{+0.9}_{-1.1} \times 10^{17}$ given the metallicity of
the background \ion{H}{2} region, which is likely a slight underestimate
of $N_{\rm HI}$. A conservative estimate of the \ion{H}{1} column
density integrated over all velocities is
$N_{\rm H I}^{\rm tot} \sim 2.5 \times 10^{19}$ cm⁻². There is a
possibility that the found column densities are in fact lower limits,
since the found \ion{Si}{2} column densities are close to the limit
where this ion becomes optically thick. We therefore conclude that the
leaked ionizing photons, if originating from this cluster, most likely
escaped via sight lines through the ionized medium, which must thus
contain a neutral gas column density
$5 \times 10^{13} \leq N_{\rm HI}^{\rm HIS} \leq 4 \times 10^{15}$. This
range is bounded downwards by the value at which HI becomes transparent
to Lyman-$\alpha$, and upwards by the sensitivity to \ion{Si}{2} of this
observation.

@@

GÖ \& MH acknowledge the support of the Swedish Research Council,
Vetenskapsrådet, and the Swedish National Space Board (SNSB) and M. H.
is an Academy Fellow of the Knut and Alice Wallenberg Foundation. This
project has made extensive use of the Python-based packages Numpy
\citep{Numpy}, SciPy \citep{SciPy}, Matplotlib \citep{Matplotlib},
Pandas \citep{Pandas}, LMfit \citep{lmfit2014}, and Astropy
\citep{Astropy2013}.
